Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-11-20 ms/ms.Rmd
ms: results - add PICP

>>>>

Although the difficulty of predicting peat depth caused prediction intervals to be wide, these uncertainty estimates were well-calibrated.
At Skrimfjella the prediction interval coverage probability was 91 %, and at Ørskogfjellet it was 84 % (both compared to the target value of 90 %).
Observations outside of the prediction intervals were evenly distributed across each of the study areas.

### 2024-11-20 ms/ms.tex
ms: results - add PICP

The spatial distribution of peat depth is often overlooked in land use planning and carbon accounting because peat depth is not mapped with sufficient coverage, resolution, or accuracy.
Maps are crucial because they link high-level targets to specific management decisions, unlike spatially-aggregated estimates \citep{oecdOECDEnvironmentalPerformance2022}.
For example, Norwegian regulations restrict conversion to farmland more strictly where peat depth exceeds \unit{1\,m}, and the distribution of peat depth on a farmer's property determines whether he is allowed to convert peatland (Forskrift om nydyrking, 1997, § 5a).
Maps also make it possible to quantify the effect of specific management decisions and thereby understand how local outcomes contribute to regional and national outcomes \citep{oecdOECDEnvironmentalPerformance2022}.

@@

>>>>

The spatial distribution of peat depth is often overlooked in land use planning and carbon accounting because peat depth is not mapped with sufficient coverage, resolution, or accuracy.
Maps are crucial because they link high-level targets to specific management decisions, unlike spatially aggregated estimates \citep{oecdOECDEnvironmentalPerformance2022}.
For example, Norwegian regulations restrict conversion to farmland more strictly where peat depth exceeds \unit{1\,m}, and the distribution of peat depth on a farmer's property determines whether he is allowed to convert peatland (Forskrift om nydyrking, 1997, § 5a).
Maps also make it possible to quantify the effect of specific management decisions and thereby understand how local outcomes contribute to regional and national outcomes \citep{oecdOECDEnvironmentalPerformance2022}.

@@

Although the difficulty of predicting peat depth caused prediction intervals to be wide, these uncertainty estimates were well-calibrated.
At Skrimfjella the prediction interval coverage probability was 91 \%, and at Ørskogfjellet it was 84 \% (both compared to the target value of 90 \%).
Observations outside of the prediction intervals were evenly distributed across each of the study areas.
